Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-06 chi2013-webbox.tex
better rel work

The user experience benefits of conquering such data integration challenges have been demonstrated in PIM prototype systems with integrative data models.  For example, the uniform query capabilities provided by SEMEX~\cite{semex} and \emph{Stuff I've Seen}\cite{stuffiveseen}, showed the speed, efficiency and re-findability gained when a user is able to quickly trace and cross-reference information about the people, places and things mentioned throughout his or her files, folders, e-mail, and other information repositories.  Similarly, Haystack \cite{haystack} demonstrated the reduced effort and increased efficiency of being able to view and re-use information easily in multiple task contexts without fragmentation or loss of consistency when a single, consolidated data model was used across applications.

Therefore, despite the multifaceted challenges of data integration, various fields have sought methods to resolve them. The database integration and Semantic Web \cite{Shadbolt:2006:SWR:1155313.1155373} fields, for example, have pursued automatic, recently machine-learning approaches to data integration, at either the level of \emph{ontology/schema-level matching}~\cite{euzenat2004api,doan2003learning}, or \emph{instance matching}~\cite{suchanek2011paris,castano2006matching}.   In contrast, the end-user programming community has pursued user-driven approaches, in which the user orchestrates the process of reconciliation at various levels of specificity.  Systems that use this approach include ``mash-up makers'' (such as Mashmaker, \cite{mashmaker}, Marmite \cite{marmite}, and Vegemite \cite{vegemite}) and visual programming languages such as Yahoo Pipes \cite{pipes}.

@@

\section{Pre-studies: Identifying Needs and Challenges}

%% not sure where this goes >> but i want to keep it

>>>>

The user experience benefits of conquering such data integration challenges have been demonstrated in PIM prototype systems with integrative data models.  For example, the uniform query capabilities provided by SEMEX~\cite{semex} and \emph{Stuff I've Seen}\cite{Dumais:2003:SIS:860435.860451}, showed the speed, efficiency and re-findability gained when a user is able to quickly trace and cross-reference information about the people, places and things mentioned throughout his or her files, folders, e-mail, and other information repositories.  Similarly, Haystack \cite{haystack} demonstrated the reduced effort and increased efficiency of being able to view and re-use information easily in multiple task contexts without fragmentation or loss of consistency when a single, consolidated data model was used across applications.

Therefore, despite the multifaceted challenges of data integration, various fields have sought methods to resolve them. The database integration and Semantic Web \cite{Shadbolt:2006:SWR:1155313.1155373} fields, for example, have pursued automatic, recently machine-learning approaches to data integration, at either the level of \emph{ontology/schema-level matching}~\cite{euzenat2004api,doan2003learning}, or \emph{instance matching}~\cite{suchanek2011paris,castano2006matching}.   In contrast, the end-user programming community has pursued user-driven approaches, in which the user orchestrates the process of reconciliation at various levels of specificity.  Systems that use this approach include ``mash-up makers'' (such as Mashmaker, \cite{intel_mashmaker}, Marmite \cite{Lin:2009:EPM:1502650.1502667}, and Vegemite \cite{Wong:2007:MMM:1240624.1240842}) and visual programming languages such as Yahoo Pipes \cite{citeulike:8887891}.

@@

\section{Pre-studies: Identifying Needs and Challenges}
%% not sure where this goes >> but i want to keep it
